EldersAIR initial home/adult data work

### 2020-02-14 dustrak_data_cleaning.Rmd
major data cleaning updates

---
title: "EldersAIR initial PM data work"
author: "Ethan Walker"
date: "Started 12 Feb 2020, Updated 12 Feb 2020"
output: pdf_document
---

@@

@@

>>>>

---
title: "EldersAIR initial PM data work"
author: "Ethan Walker"
date: "Started 12 Feb 2020, Updated 14 Feb 2020"
output: pdf_document
---

@@

# Load, format, and save DustTrak log file for NP
```{r}
## Box location: Update Box location once final data loaded
np_dustrack_initial <- read_csv("Input/NP/np_dustrack_20200214.csv") %>% 
  # rename variables
  mutate(home_winter_id = as.factor(HomeWinterID),
         dtid = as.factor(DTID),
         start_date_pm = mdy(StartDate),
         start_time_pm = as.character(StartTime),
         stop_date_pm = mdy(StopDate),
         stop_time_pm = as.character(StopTime),
         sample_obs = as.numeric(DTLength),
         sample_ave = as.numeric(DTAverage),
         sample_min = as.numeric(DTMin),
         sample_max = as.numeric(DTMax),
         pm_comments = as.character(Comments),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)
#write_rds(np_dustrack_initial, "Output/np_dustrack.rds")
```

@@

# Initial cleaning steps
## Remember to add correction factor
```{r}
elders_pm_full_raw <- read_rds("Output/elders_pm_full_raw.rds")
```

### 2020-02-14 home_adult_data_cleaning.Rmd
major data cleaning updates

---
title: "EldersAIR initial home/adult data work"
author: "Ethan Walker"
date: "Started 10 Feb 2020, Updated 10 Feb 2020"
output: pdf_document
---

@@

# Load, format, and save home and adult overview/demographic data for NP
```{r}
# Load files 
## Box location: Update Box location once final data loaded
np_adult_initial <- read_csv("Input/NP/np_adults_20200210.csv") %>% 
  rename_all(tolower) %>% 
  mutate(adult_hwid = as.factor(adulthwid),
         home_id = as.factor(homeid),
         adult_id = as.factor(adultid),
         home_winter_id = as.factor(homewinterid)) %>% 
  select(adult_hwid, home_id, adult_id, home_winter_id)

## Box location: Update Box location once final data loaded
np_home_initial <- read_csv("Input/NP/np_home_20200210.csv") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = ymd(interventiondate),
         intervention_time = as.character(interventiontime),
         sampling_date_1 = ymd(samplingdate),
         sampling_time_1 = as.character(samplingtime),
         pickup_date_1 = ymd(pickupdate),
         pickup_time_1 = as.character(pickuptime),
         sampling_date_2 = ymd(sampling2date),
         sampling_time_2 = as.character(sampling2time),
         pickup_date_2 = ymd(pickup2date),
         pickup_time_2 = as.character(pickup2time),
         home_qaqc_comments = as.character(qaqchccomments)) %>% 
  select(home_id, winter_id, home_winter_id, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2,
         home_qaqc_comments) 
```

>>>>

---
title: "EldersAIR initial home/adult data work"
author: "Ethan Walker"
date: "Started 10 Feb 2020, Updated 14 Feb 2020"
output: pdf_document
---

@@

# Load, format, and save home and adult overview/demographic data for NP
```{r}
# Load files 
## Box location: Update Box location once final data loaded
np_adult_initial <- read_csv("Input/NP/np_adults_20200214.csv") %>% 
  rename_all(tolower) %>% 
  mutate(adult_id_num = as.factor(adultid),
         home_id = as.factor(homeid),
         adult_id_char = as.factor(id),
         hispanic = as.factor(hispanic),
         race = as.factor(race),
         gender = as.factor(gender),
         consent_date = mdy(consentdate)) %>% 
  select(adult_id_num, home_id, adult_id_char, hispanic, race, gender, consent_date) %>% 
  arrange(adult_id_num)
#write_rds(np_adult_initial, "Output/np_adult.rds")

## Box location: Update Box location once final data loaded
np_homewinter_initial <- read_csv("Input/NP/np_homewinter_20200214.csv") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         winter_id = as.factor(winterid),
         home_winter_id = as.factor(homewinterid),
         intervention_date = mdy(interventiondate),
         intervention_time = as.character(interventiontime),
         sampling_date_1 = mdy(samplingdate),
         sampling_time_1 = as.character(samplingtime),
         pickup_date_1 = mdy(pickupdate),
         pickup_time_1 = as.character(pickuptime),
         sampling_date_2 = mdy(sampling2date),
         sampling_time_2 = as.character(sampling2time),
         pickup_date_2 = mdy(pickup2date),
         pickup_time_2 = as.character(pickup2time)) %>% 
  select(home_id, winter_id, home_winter_id, intervention_date, intervention_time,
         sampling_date_1, sampling_time_1, pickup_date_1, pickup_time_1,
         sampling_date_2, sampling_time_2, pickup_date_2, pickup_time_2) %>% 
  filter(!is.na(home_id)) %>% 
  arrange(home_id, winter_id)
#write_rds(np_homewinter_initial, "Output/np_homewinter.rds")

## Box location: Update Box location once final data loaded
np_home_initial <- read_csv("Input/NP/np_home_20200214.csv") %>% 
  rename_all(tolower) %>% 
  mutate(home_id = as.factor(homeid),
         home = as.factor(home),
         treatment = as.factor(txcondition)) %>% 
  select(home_id, home, treatment)
#write_rds(np_home_initial, "Output/np_home.rds")
```

# Combine adult, home, homewinter files
```{r}
np_ids_linked <- np_homewinter_initial %>% 
  left_join(np_home_initial, by = c("home_id")) %>% 
  left_join(np_adult_initial, by = c("home_id")) 
#write_rds(np_ids_linked, "Output/np_ids_linked.rds")
```
